Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-03 docs/ms.tex
Update ms.tex

We assume Lensed galaxy ellipticity $\epsilon_{\ell}$ is related
to the intrinsic galaxy ellipticity $\epsilon_{0}$ in the weak lensing
regime via 
\begin{equation}
\epsilon_{\ell}=\frac{\epsilon_{0}+g}{1+g^{*}\epsilon_{0}}
\end{equation}

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a - b)/(a + b) exp(2i$\phi$). Due
to the isotropicity of Universe ,we expect $\phi$ has a uniform distribution
from 0 to $\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

Therefore $<\epsilon_{\ell}>$ can be adopted as an estimator of g.

>>>>

We assume the lensed galaxy ellipticity $\epsilon_{\ell}$ is related
to the intrinsic galaxy ellipticity $\epsilon_{0}$ in the weak lensing
regime via 
\begin{equation}
\epsilon_{\ell}=\frac{\epsilon_{0}+g}{1+g^{*}\epsilon_{0}}
\end{equation}

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. In weak lensing region we have 
\begin{equation}
g=\frac{\gamma}{1-k}\approx\gamma
\end{equation}
$\gamma$ is the shear .This is the assumption we use through out
the paper.$\epsilon$ is defined in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as
\begin{equation}
\epsilon=\frac{a-b}{a+b}e^{2i\phi}
\end{equation}
Due to the isotropicity of Universe ,for the unlensed ellipticity $\epsilon_{0}$ 
we expect $\phi$ has a uniform distribution
from 0 to $\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}
Therefore $<\epsilon_{\ell}>$ can be adopted as an estimator of g.
